---
title: "Where Shall We Retire ?"
author: "J.E.Black"
date: "December 4, 2016"
output: ioslides_presentation
---

---
## Background

* As of 2014, about 4 million people retire every year.
* Some states are more "Retirement Friendly" than others.
* In Mar 2015, "BankRate" published a "First to Worst" survey, ranking states according to:
    + Cost of Living
    + Crime Rate
    + Health Care Quality
    + Weather
    + Well-being
* According to the BankRate survey, 60% of retirees will move when they retire.

## Obtaining the Data

* We "scraped" the "First to Worst" data from the "BankRate" website at: 
"http://www.bankrate.com/finance/retirement/best-places-retire-how-state-ranks.aspx""

* After minor data cleanup, and adding the standard Postal Code State Abbreviations, 
we were ready to visualize the data.

* We loaded the required libraries as needed: 
```{r setup, echo=TRUE, message=FALSE}
if (!require("plotly")) install.packages("plotly")
library(plotly)
if (!require("webshot")) install.packages("webshot")
library(webshot)
```

## Test Slide Two Do the Data

```{r doData}
# Create data frame
state_pop <- data.frame(State = state.abb, Pop = as.vector(state.x77[,1]))
# Create hover text
state_pop$hover <- with(state_pop, paste(State,'<br>', "Population:", Pop))
# Make state borders black
borders <- list(color = toRGB("black"), width=2)
# Set up some mapping options
map_options <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = toRGB('black')
)
```

## Test Slide Three with Plot

```{r plotData}
plotly::plot_ly(state_pop, z = state_pop$Pop, text = state_pop$hover, locations = state_pop$State, type = 'choropleth', locationmode = 'USA-states', color = state_pop$Pop, colors = 'Blues', marker = list(line = borders)) %>%
  colorbar(title = "Population") %>%
  layout(title = 'US Population in 1975<br>(Hover for Details)', geo = map_options)
```


